Constraints on the mass and occupation fraction of dark matter halos hosting Lyman-alpha emitters at $z\sim 3$

### 2013-06-26 paper/ms.tex
first full draft version

\title[Halo mass and occupation fraction for LAEs at
  $z=3.1$]{Constraints on the mass and occupation
  fraction of dark matter halos hosting Lyman-alpha emitters
  at $z$=3.1}    
\author[~J.~E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright 
Jaime E. Forero-Romero$^{1}$ and
Julian Mej\'ia-Restrepo$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el
Observatorio 1515, Santiago, Chile}

@@

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$, by comparing the  number density and the angular
correlation function between mock and observed fields. The mock fields
are constructed in a large cosmological N-body simulation using a
model where a dark matter halo can only host one LAE with a
probability $f_{\rm occ}$ if its mass is found within the mass range
delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
conclude that the number density and spatial clustering information
available are not sufficient to derive a unique and narrow set of
values for the parameter in the model. We find three different
families of models based on their mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}< 1.0$ dex and occupation
fraction $f_{\rm occ}$.  The dominant familiy is composed by models with a narrow
mass range $\Delta M<1.0$ dex, a low occupation fraction $f_{\rm occ}\leq 0.3$
and a maximum mass $M_{\rm max}< 10^{12}$\hMsun.  This finding
suggests that the most massive dark matter halos at that epoch do not
host the brightest LAEs. This also gives support to observational evidence
concluding that only a small fraction of star forming galaxies can be
actually detected as LAEs. We provide tables and mock catalogs for the
succesful models.

\end{abstract}

\begin{keywords}
{galaxies: kinematics and dynamics, Local Group, methods:numerical}
\end{keywords}

@@

Some theoretical approaches to this problem have been based on a
forward modeling. Starting from the DM halo population, the
corresponding intrinsic star formation properties are infered and
statistics such as the luminosity function, the correlation function
and the equivalent width distributions. Such modelling has been
implemented from analytic considerations, semi-analytic models
 and 
full N-body hidrodynamical simulations
\citep{Dayal2009, ForeroRomero2011, Yajima2012, ForeroRomero2012} .

Added to the uncertainties in the astrophysical processeses describing
star formation in galactic populations, a highly debated steps in this
approach is the calculation of the fraction of Lyman-$\alpha$ photons
that escape the galaxy to the observer. Given the resonance nature of
the line, the radiative transfer of Lyman-$\alpha$ is sensitive to the
density, temperature, topology and kinematics of the neutral Hydrogen
in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011,
Laursen2013}.

This complexity makes the use of monte-carlo simulations for the
radiative transfer a required tool to obtain physically sound results,
although the degeneracy in the physical parameters involved in the
problem makes it difficult to achieve a robust consensus on what is
the theoretical expected value for the Lyman-$alpha$ escape fraction
in high redshift.

@@

Our method to constrain the typical mass of a dark matter halos
hosting LAEs at $z=3.1$ is based on the comparison of observational
results on the surface number density and the predictions of a simple
model that uses the outputs from cosmological N-body simulations.

In the next subsections we describe in detail the four key elements of
this workflow. First, we present the observations we take as a
benchmark. Second, the N-body simulation and the halo catalogs we
use. Third, the simplified model that allows us to translated halo
catalogs into mock LAE observations. Fourth, the statistics we use to
compare observational results against our theoretical predictions.

@@

The observational benchamark we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey  conducted with
the Subaru 8.2m telescope and the Subaru Prime Focus Camera, which has
a field of view covering $34\times 27$ arcmin, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$. The narrow
band filter is centered at $4977$ \AA with  $77$\AA width,
corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc
$h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors report a total  $2161$ LAEs with an
observed equivalent width larger than $190$\ over a total survey area
of $2.42$ deg$^{2}$, this corresponds to  averaga surface number
density of $0.20\pm 0.01$ arcmin$^{-2}$.

The survey covered four independent fields. The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs, this field has been
known to harbor a region with a large density excess of galaxies. The
second observed region is composed by the fields Subaru/{\it
  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a 
total of $0.58$ deg$^2$ and $386$ LAEs. The third and fourth fields
are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs,
and the fild arotund the Great Observatory Optical Deep Survey North
(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs.

There is abundant observational work done on LAEs at redshift $z=3.1$
\citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
However, we decide to focus on the data from \cite{Yamada2012} because
it has the largest covered area with homogeneous intrumentational
conditions (telescope, narrow band filter), data reduction pipeline
and conditions to construct the LAE catalog. This ensures that the
number density variations among fields are due only to
astrophysical reasons and not different observational conditions or
criteria to construct the catalogs.

@@

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking lenght of 0.17 times the interparticle
distance. The minimum halo mass in the models we construct in this \documentname
correspond to groups of $\sim 75$ particles. The catalogs were
obtained from the publicly available Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
We focus our work on halos more massive than $1\times 10^{10}$\hMsun
that are resolved with at least $70$ particles.

@@

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bounds for the mass range $M_{\rm min}<
M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. We do not assign a
luminosity to each LAE. We are primaraly interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.

For each model ${\mathcal M}$ we create a set of mock fields from
disjoint volumes in the simulation. Each volume has the same geometry
probed by Suprime-CAM and the narrow band filter, namely rectangular
cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
the last dinemsion goes in the redshift direction. This corresponds to
a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
$5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
simulation. In each mock field a LAE is assigned to the position of a
dark matter halo if the halo mass is in the range allowed by the model
$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from
an homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
fraction $\xi<f_{\rm occ}$.

Next we construct mock surveys by making groups of $11$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping is done in two
different ways. In the first way, called {\texttt match}, we follow
the clustering of the observed fields. From the $11$ mock fields, $7$
are constructed from contigous fields in the simulation to mimic the
SSA22 region, $3$ are also contiguous between them but not to the first
$7$ fields to mimic the SXDS fields and finally $2$ non-contigous
fields to imitate the SDF and GOODS-North field. Our main goal with
this selection is to test the impact on the final statistics of having
$7$ clustered fields. The second way to group the mock fields is called {\texttt
  random}, whereby all the $11$ fields are selected in such a way as
to avoid that any two volumes are contigous.

@@

We make a thorough exploration of the parameter space for the models
${\mathcal M}$. $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
to $12.9$ with an even spacing of $0.1$ dex. $\log_{10} M_{\rm max}$
takes values in the same range as $\log_{10}M_{\rm min}$ only with a
displacement of $0.1$ dex in the whole range. The occupation fraction
$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regulary
spaced by $0.1$. In total the number of different models ${\mathcal
  M}$ that are explored is $30 \times 30 \times 10 = 9000$.

For each mock survey generated in a given model ${\mathcal M}$ we
compute the surface density in the $12$ mock fields. We perform a
Kolmogorov-Smirnov (KS) to compare this mock date against the $12$
observational values. From this test we obtain a value $0<P<1$ to
reject the null hypotesis, namely that two data sets come from the
same distribution. In this paper we consider that for values $P>0.05$
the two distributions can be thought as coming from the same
distribution.

In this paper we consider that a model
${\mathcal M}$ that has at least one (1) mock survey (out of 15)
consistent with the observed distribution of LAE number densities has
viable parameters thatdeserve to be considered for further analysis.

\section{Basic Results}

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{fig:halos} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents on of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal grey band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

@@

This result provides the basis to understand why a range of models
${\mathcal M}$ can be expected to be consistent with
observations. In Figure \ref{fig:halos} we can read that models
with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
surface number density lower than the observational
constrain. The oppossite is true in models with $\log_{10} M_{\rm min}<10.5$
that will show surface number density larger than observations, this
implies that in such models the occupation fraction has to be tuned
$f_{\rm occ}<1.0$ as to lower the halo numeber density to match the
gray band values.

Conversely, there are regions in the plot where the halo surface
density is always higher than the observational constraints correspond
to models ${\mathcal M}$ with a minimum mass below $M_{\rm min}<
3\times 10^{10}$\hMsun. Models with this minimum mass hava a chance
for successfuly reproducing observations if the occupation fraction
$f_{\rm occ}<1$ is tuned as to lower the halo number density down to
the observed value.

In the next subsection we quantify this intuition by means of the KS
tests between mock surveys and observations.

@@

In Figure \ref{fig:landscale} there are three regions of parameter
space that can be clearly distinguised. The first region corresponds
to models where the minimum mass is high $\log_{10}M_{\rm min}>
11.5$. None of this models is compatible with observations as expected
from the results in the previous section. For these models the number
density of LAEs is too low.

The second region corresponds to an intermediate range for the minimum
mass $10.5<\log_{10}M_{\rm min}<11.5$ where regardless of the value of
the maximum mass $M_{\rm max}$ it is possible to tune the occupation
fraction $f_{\rm occ}$ to bring some of the mock observations into
good agreement with observations. In this region in parameter space
one can thus find two extreme kinds of models.  One kind where the
mass interval is very narrow with sizes smaller than $<0.3$ dex (a
factor of two in mass) and others where the mass interval is very
extended, larger than $1.0$ dex, going up to the maximum halo mass
present in the simulation at that redshift.

The third region in parameter space corresponds to $\log_{10}M_{\rm
  min}<10.5$. In this case only models with a narrow mass interval of
at most $0.5$ dex ($\log_{10}M_{\rm max}<11.0$) and low
occupation fractions $f_{\rm occ}<0.3$ are allowed.

Without any additional information our method allows us to infer that
most of the succesful models are found in the second and third region of
parameter space where. This result was already expected from halo
abundance calculations shown in Figure \ref{fig:halos}. In the next
section we reduce the size of this region by using more stringent
constraints to define the agreement with observations and the
inclusion of the angular correlation function information by
\cite{Hayashino2004}.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a mininium number of mock survey
  realizations that are consistent with observations.
  \label{fig:high_success_rate}.}  
\end{figure*}

@@

Figure \ref{fig:high_success_rate} shows the number of models
that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
{\texttt  match} and {\texttt random} methods.  This shows that there
are between $80$ to $100$ models with all the 15 realizations with
$P>0.05$. Selction of these models as successful represents a
reduction of a factor of $\sim 6$ with repect to the total number of
mocks with at least one consistent mock.

@@

\subsection{Consitency with the Angular Correlation Function}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf} 
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\gamma$) of the 
mean angular correlation function of the 15 mock surveys for each
model. Blue dots corresponds to simulations and the green cross to
observations by \citet{Hayashino2004}. The error bars in the
theoretical data correspond to the starndard deviation from the
different mocks. Right: Same results as before in the
$\theta_{0}$-$M_{\rm min}$ plane. This time the observational
constraints are represented by the red rectangle. Blue squares
represent models with $\log_{10} M_{\rm  max}<12.0$, green circles are
models with $\log_{10} M_{\rm max}>12.0$.
\label{figure:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
\end{center}
\caption{Best models paramter space when both the constraints on the
  maximal number of  consistent mocks and the occupation  fraction
  $f_{\rm occ}\leq  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$
  (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth).
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

We now make a further selection to the models compatible with the
observational angular correlation function (ACF). The measurementens
presented in \citep{Yamada2012} do not report an ACF
measurement. Instead we use the results reported by
\citep{Hayashino2004} on the LAEs observed in the densest field of
SSA22.

It is important to keep in mind that there are some differences
between this work and \citep{Yamada2012}. First, the color selection by
\cite{Yamada2012} is less stringent compared to the one by
\cite{Hayashino2004}. Also the EW threshold is different,
\cite{Hayashino2004} uses a cut around $154$\AA instead of $190$\AA
used by \citep{Yamada2012}

The comparison between the theoretical and observational ACF is done in
therms of the angular correlation lenght obtained  by fitting to a power-law
function:

\begin{equation}
\xi(\theta) = \left(\frac{r}{\theta_{0}}\right)^{-\gamma}
\end{equation}

Both the theoretical and observational ACF are derived by a least
square minimization procedure. The results are shown  in Figure
\ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$  plane
where the average and standard deviation for each mock is shown in
comparison with the resut derived from observations.  The Error bars in
these figures represents the standard deviation of the ACF over all
the sub-fields in the 15 mock observations. These error bars are
larger than the statistical uncertainty from the fitting procedure on
a single field..

We see in the left panel Figure \ref{figure:correlation_parameters} that
the observational ACF measured by \cite{Hayashino2004} (green dot) is
succesul in reducing the total number of possible models. Only those
with angular-correlation length within
$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are consideret to
reproduce observations.

>>>>

\title[Halo mass and occupation fraction for LAEs at
  $z=3.1$]{Constraints on the mass and occupation
  fraction of dark matter halos hosting Lyman-alpha emitters
  at $z\sim 3$}    
\author[~J.~E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright 
Jaime E. Forero-Romero$^{1}$ and
Julian Mej\'ia-Restrepo$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el
Observatorio 1515, Santiago, Chile}

@@

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$, by comparing the number density and the angular
correlation function between mock and observed fields. The mock fields
are constructed in a large cosmological N-body simulation using a
model where a dark matter halo can only host one LAE with a
probability $f_{\rm occ}$ if its mass is within the mass range
delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
conclude that the number density and spatial clustering information
available from observations is not sufficient to derive a unique and narrow set of
values for the parameters in the model. We find three different
families of models based on their mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
fraction $f_{\rm occ}$.  However, there is a dominant familiy composed
by models with a narrow mass range $\Delta M<1.0$ dex, a low
occupation fraction $f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm
  max}< 10^{12}$\hMsun.  This finding suggests that the most massive
dark matter halos at that epoch do not host the brightest LAEs. This
also gives support to observational evidence concluding that only a
small fraction of star forming galaxies can be actually detected as
LAEs. We provide tables and mock catalogs for the successful models. 
\end{abstract}

\begin{keywords}
{cosmology: theory – cosmology: large-scale structure of universe –
  galaxies: formation – galaxies: high-redshift – galaxies: statistics
  – galaxy: haloes} 
\end{keywords}

@@

Some theoretical approaches to this problem have been based on
ab-initio approach modeling. Starting from the DM halo population, the
corresponding intrinsic star formation properties are inferred
together with other statistics such as the luminosity function, the
correlation function and the equivalent width distributions. Such
modelling has been implemented from analytic considerations,
semi-analytic models  and  full N-body hidrodynamical simulations
\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012, Orsi2012}.

Added to the uncertainties in the astrophysical processes describing
star formation in galactic populations, a highly debated step in this
approach is the calculation of the fraction of \ly photons
that escape the galaxy to the observer. Given the resonant nature of
the \lya line, the radiative transfer of \ly is sensitive to the
density, temperature, topology and kinematics of the neutral Hydrogen
in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011, Dijkstra2012,
Laursen2013}.

This complexity makes the use of monte-carlo simulations for the
radiative transfer a required tool to obtain physically sound results,
although the degeneracy in the physical parameters involved in the
problem makes it difficult to achieve a robust consensus on what is
the theoretical expected value for the \ly escape fraction
at high redshift.

Our objective in the present \documentname is to use a method to
bypass all the complexity involved in the estimation of the \ly escape
fraction to infer information relevant to the understanding of LAEs in
a cosmological context. The analysis we present is thus based on one
of the most robust prediction of $\Lambda$CDM, namely the clustering
and abudance of dark matter halos. We construct a simple model that
allow us to construct mock catalogs and explore a wide range of
parameters to narrow the mass interval of halos hosting LAEs together
with its occupation fraction.

Another central point in our study is the explicit inclusion of cosmic
variance effects by using large volume cosmological simulations. This
allows us to go closer to the space of observables and directly
explore the compatibility of a model with observations.

This paper is structured as follows. In the next section we present
the simulation and model used to produce the mock catalogs and the criteria
used to compare them against observations. In \SS \ref{sec:results} we
present the main results in terms of the parameters of our model. We
continue with a discussion of these results under the light of other
observational results for LAEs and abundance matching models for
galaxy formation before presenting our conclusions in \SS
\ref{sec:conclusions}.

@@

Our method is based on the comparison of observatios and mock
catalogs on the surface number density and the angular correlation
function.  In the next subsections we describe in detail the four key
elements of this workflow. First, we present the observations we take
as a benchmark. Second, the N-body simulation and the halo catalogs we
use. Third, the simplified model that allows us to translated halo
catalogs into mock LAE observations. Fourth, the statistics we use to
compare observational results against our theoretical predictions.

@@

One of the main observational benchmarks we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey  conducted with
the Subaru 8.2m telescope and the Subaru Prime Focus Camera, which has
a field of view covering $34\times 27$ arcmin, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$. The narrow
band filter is centered at $4977$ \AA with  $77$\AA width,
corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc
$h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors report a total  $2161$ LAEs with an
observed equivalent width larger than $190$\ over a total survey area
of $2.42$ deg$^{2}$, this corresponds to  average surface number
density of $0.20\pm 0.01$ arcmin$^{-2}$.

The survey covered four independent fields. The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs, this field has been
known to harbor a region with a large density excess of galaxies. The
second observed region is composed by the fields Subaru/{\it
  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a 
total of $0.58$ deg$^2$ and $386$ LAEs. The third and fourth fields
are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs,
and the field around the Great Observatory Optical Deep Survey North
(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs.

There is abundant observational work done on LAEs at redshift $z=3.1$
\citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
However, we decide to focus on the data from \cite{Yamada2012} because
it has the largest covered area with homogeneous instrumentation
conditions (telescope, narrow band filter), data reduction pipeline
and conditions to construct the LAE catalog. This ensures that the
number density variations among fields are due only to
astrophysical reasons and not different observational conditions or
criteria to construct the catalogs.

@@

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking length of 0.17 times the inter-particle
distance. The minimum halo mass in the models we construct in this \documentname
correspond to groups of $\sim 75$ particles. The catalogs were
obtained from the publicly available Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
We focus our work on halos more massive than $1\times 10^{10}$\hMsun
that are resolved with at least $70$ particles.

@@

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bounds for the mass range $M_{\rm min}<
M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. We do not assign a
luminosity to each LAE. We are primarily interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.

For each model ${\mathcal M}$ we create a set of mock fields from
disjoint volumes in the simulation. Each volume has the same geometry
probed by Suprime-CAM and the narrow band filter, namely rectangular
cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
the last dimension goes in the redshift direction. This corresponds to
a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
$5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
simulation. In each mock field a LAE is assigned to the position of a
dark matter halo if the halo mass is in the range allowed by the model
$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from
an homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
fraction $\xi<f_{\rm occ}$.

Next we construct mock surveys by making groups of $11$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping is done in two
different ways. In the first way, called {\texttt match}, we follow
the clustering of the observed fields. From the $11$ mock fields, $7$
are constructed from contiguous fields in the simulation to mimic the
SSA22 region, $3$ are also contiguous between them but not to the first
$7$ fields to mimic the SXDS fields and finally $2$ non-contiguous
fields to imitate the SDF and GOODS-North field. Our main goal with
this selection is to test the impact on the final statistics of having
$7$ clustered fields. The second way to group the mock fields is called {\texttt
  random}, whereby all the $11$ fields are selected in such a way as
to avoid that any two volumes are contiguous.

The second benchmark is the angular correlation function (ACF). The
measurements presented in \citep{Yamada2012} do not report an ACF
measurement. Instead we use the results reported by
\citep{Hayashino2004} on the LAEs observed in the densest field of
SSA22. It is important to keep in mind that there are some differences
between this work and \citep{Yamada2012}. First, the color selection by
\cite{Yamada2012} is less stringent compared to the one by
\cite{Hayashino2004}. Also the EW threshold is different,
\cite{Hayashino2004} uses a cut around $154$\AA instead of $190$\AA
used by \citep{Yamada2012}

@@

We make a thorough exploration of the parameter space for the models
${\mathcal M}$. $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
to $12.9$ with an even spacing of $0.1$ dex. $\log_{10} M_{\rm max}$
takes values in the same range as $\log_{10}M_{\rm min}$ only with a
displacement of $0.1$ dex in the whole range. The occupation fraction
$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regularly
spaced by $0.1$. In total the number of different models ${\mathcal
  M}$ that are explored is $30 \times 30 \times 10 = 9000$.

For each mock survey generated in a given model ${\mathcal M}$ we
compute the surface density in the $12$ mock fields. We perform a
Kolmogorov-Smirnov (KS) to compare this mock date against the $12$
observational values. From this test we obtain a value $0<P<1$ to
reject the null hypothesis, namely that two data sets come from the
same distribution. In this paper we consider that for values $P>0.05$
the two distributions can be thought as coming from the same
distribution.

We begin by considering that  a model ${\mathcal M}$ that has at least
one (1) mock survey (out of 15) consistent with the observed
distribution of LAE number densities has viable parameters that
deserve to be considered for further analysis. Later on we impose
harder constraints to reduce the number of models by asking that all
the 15 mocks to be consistent with observations.

The comparison between the theoretical and observational ACF is done
in therms of the angular correlation length obtained  by fitting to a power-law
function:

\begin{equation}
\xi(\theta) = \left(\frac{r}{\theta_{0}}\right)^{-\gamma}
\label{eq:fitting}
\end{equation}

Both the theoretical and observational ACF are derived by a least
square minimization procedure. We consider that a model is consistent
with observations if the two parameters $\gamma$ and $\theta_0$ are
equal within a $1$-$\sigma$ range.

\section{Results}
\label{sec:results}

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{fig:halos} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents on of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal gray band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

@@

This result provides the basis to understand why only a specific range of models
${\mathcal M}$ can be expected to be consistent with
observations. From Figure \ref{fig:halos} we can read that models
with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
surface number density lower than the observational
constrain. This makes impossible that models with that minimum mass
can be compatible with observations.

The opposite is true in models with $\log_{10} M_{\rm min}<10.5$
that will show surface number density larger than observations, this
implies that in such models the occupation fraction has to be tuned
$f_{\rm occ}<1.0$ as to lower the halo number density to match the
gray band values.

In the next subsection we quantify this intuition by means of the
Kolmogorov-Smirnov tests between mock surveys and observations.

@@

In Figure \ref{fig:landscape} there are three regions of parameter
space that can be clearly distinguished. The first region corresponds
to models where the minimum mass is high $\log_{10}M_{\rm min}>
11.5$. None of this models is compatible with observations as expected
from the results in the previous subsection. For these models the number
density of LAEs is too low compared to observations.

The second region corresponds to an intermediate range for the minimum
mass $10.5<\log_{10}M_{\rm min}<11.5$ where regardless of the value of
the maximum mass $M_{\rm max}$ it is possible to tune the occupation
fraction $f_{\rm occ}$ to bring some of the mock observations into
good agreement with observations. In this region in parameter space
one can thus find two extreme kinds of models.  One kind where the
mass interval is very narrow with sizes smaller than $<0.3$ dex (a
factor of two in mass) and others where the mass interval is 
extended, larger than $1.0$ dex, going up to the maximum halo mass
present in the simulation at that redshift.

The third region in parameter space corresponds to $\log_{10}M_{\rm
  min}<10.5$. In this case only models with a very narrow mass interval of
at most $0.5$ dex ($\log_{10}M_{\rm max}<11.0$) and low
occupation fractions $f_{\rm occ}<0.3$ are allowed.

Without any additional information our method allows us to infer that
most of the successful models are found in the second and third region of
parameter space where. This result was already expected from halo
abundance calculations shown in Figure \ref{fig:halos}. In the next
section we reduce the size of this region by imposing tighter
constraints on the KS tests and consistency with the angular
correlation function.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a minimum number of mock survey
  realizations that are consistent with observations.
  \label{fig:high_success_rate}.}  
\end{figure*}

@@

Figure \ref{fig:high_success_rate} shows the number of models
that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
{\texttt  match} and {\texttt random} methods.  This shows that there
are between $80$ to $100$ models with all the 15 realizations with
$P>0.05$. Selection of these models as successful represents a
reduction of a factor of $\sim 6$ with respect to the total number of
mocks with at least one consistent mock.

@@

\subsection{Consistency with the Angular Correlation Function}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf} 
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\gamma$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the mean angular
correlation function. Blue dots correspond to simulations and the green cross to
observations by \citet{Hayashino2004}. The error bars in the 
theoretical data correspond to the standard deviation from the
different mocks surveys. Right: Same results as before in the shown in
the $\theta_{0}$-$M_{\rm min}$ plane. This time the observational
constraints are represented by the red rectangle. Blue squares
represent models with $\log_{10} M_{\rm  max}<12.0$, green circles
correspond to models with $\log_{10} M_{\rm max}>12.0$. 
\label{figure:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
\end{center}
\caption{Best models parameter space when both the constraints on the
  maximal number of  consistent mocks and the occupation  fraction
  $f_{\rm occ}\leq  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$
  (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth).
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

Figure \ref{figure:correlation_parameters} shows the main results in a
$\theta_{0}-\gamma$  plane where the average and standard deviation
for each mock is shown in comparison with the result derived from
observations.  The error bars in this Figure represents the standard
deviation of the ACF over all the sub-fields in the 15 mock
observations. These error bars are larger than the statistical
uncertainty from the fitting procedure on a single field.

In the left panel Figure \ref{figure:correlation_parameters} we see how
the observational ACF measured by \cite{Hayashino2004} (green dot) is
successful in reducing the total number of possible models. Only those
with angular-correlation length within
$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
reproduce observations.

In order to better illustrate the results from this test we
show in the right panel of Figure \ref{figure:correlation_parameters} 
the plane $\theta_{0}$-$M_{\rm min}$ for all models. There we divide
the models into two disjoint sets: those with $\log \frac{M_{\rm
    max}}{M_{\odot}}<12$ (blue dots) and $\log \frac{M_{\rm
    max}}{M_{\odot}}>12$ (green dots). The colored rectangle includes
the parameter region which is consistent with the observational
constraint in $\theta_{0}$. With this restriction we find that most
models with $\log \frac{M_{\rm max}}{M_{\odot}}>12$ and  $\log
\frac{M_{\rm     min}}{M_{\odot}}>11.1$ can be safely ruled out.

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraints 
in the occupation fraction and the ACF. Here we consider a model
consistent if there is an overlap of $1-sigma$ in its values for the
correlation length $\theta_0$ and the power $\gamma$ in the
correlation function.
